### 2010-01-25 doc/tech_doc/a-rex/arex_tech_doc.tex
use common logging package in cache-clean, and add conf option to specify log level. Partially fixes bug 1383
dont delete cache files that have hard links (bug 1748)

The per-job directory is only readable by the local user running the
job, and the cache directory is readable only by the A-REX user. This
means that the local user cannot access any other users' cache
files. It also means that cache files can be removed without needing
to know whether they are in use by a currently running
job. \textbf{IMPORTANT:} If a cache is mounted from an NFS server and
the GM is run by the root user, the server must have the
\emph{no\_root\_squash} option set for the GM host in the
\emph{/etc/exports} file, otherwise the GM will not be able to create
the required directories. Note that when running A-REX under a
non-privileged user account, all cache files will be owned and
accessible by the same user, and therefore modifyable by running
jobs. This is potentially dangerous and so cacheing should be used
with caution in this case.

@@

Caches can be added to and removed from the configuration as required
without affecting any cached data, but after changing the
configuration file, the A-REX should be restarted. If a cache is to be
removed and all data erased, it is recommended that the cache be put
in a \emph{draining} state until all currently running jobs possibly
accessing files in this cache have finished. In this state the cache
will not be used by any new jobs, but the hard links in the
\emph{joblinks} directory will be cleaned up as each job
finishes. Once this directory is empty it is safe to delete the entire
cache. See the \emph{cachedir} option in
Section~\ref{SubSection: ConfigFile} for how to set a cache to a
draining state.

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finishes (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}. The minumum value
for both parameters is 2 hours.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
-- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by using
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to
  the directory in which the SD is created. If \emph{path} is {*} the
  default sessiondir is used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} --
  specifies a directory to store cached data (see section
  \ref{sec:cache}). Multiple cache directories may be specified by
  specifying multiple \emph{cachedir} commands. Cached data will be
  distributed over multiple caches according to free space in
  each. Specifying no \emph{cachedir} command or commands with an
  empty path disables caching. The optional \textit{link\_path} specifies
  the path at which \emph{path} is accessible on computing nodes, if
  it is different from the path on the A-REX host. If
  \textit{link\_path} is set to '.'  files are not soft-linked, nor
  are per-job links created, but files are copied to the session
  directory. If a cache directory needs to be drained, then
  \emph{cachedir} should specify \emph{``drain''} as the
  \emph{link\_path}.
\item \textbf{\textit{remotecachedir}}\textit{=path {[}link\_path]} -
  specifies caches which are under the control of other A-REXs, but which
  this A-REX can have read-only access to (see
  Section~\ref{sec:remotecaches}).  Multiple remote cache directories may be
  specified by specifying multiple \emph{remotecachedir} commands. If
  a file is not available in paths specified by cachedir, the GM looks
  in remote caches. \emph{link\_path} has the same meaning as in
  \emph{cachedir}, but the special path ``replicate'' means files will
  be replicated from remote caches to local caches when they are requested.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} --
  specifies high and low watermarks for space used on the file system
  on which the cache directory is located, as a percentage of total
  file system capacity. When the max is exceeded, files will be
  deleted to bring the used space down to the min level. It is a good
  idea to have each cache on its own separate file system. To turn off
  this feature, \char`\"{}cachesize\char`\"{} without parameters can
  be specified. These cache settings apply to all caches specified by
  \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. The actual
number is provided in job description and defaults to 0.
\end{itemize}

>>>>

The per-job directory is only readable by the local user running the
job, and the cache directory is readable only by the A-REX user. This
means that the local user cannot access any other users' cache
files. It also means that cache files can be removed without needing
to know whether they are in use by a currently running job. However,
as deleting a file which has hard links does not free space on the
disk, cache files are not deleted until all per-job hard links are
deleted. \textbf{IMPORTANT:} If a cache is mounted from an NFS server
and the A-REX is run by the root user, the server must have the
\emph{no\_root\_squash} option set for the A-REX host in the
\emph{/etc/exports} file, otherwise the A-REX will not be able to
create the required directories. Note that when running A-REX under a
non-privileged user account, all cache files will be owned and
accessible by the same user, and therefore modifyable by running
jobs. This is potentially dangerous and so cacheing should be used
with caution in this case.

@@

Caches can be added to and removed from the configuration as required
without affecting any cached data, but after changing the
configuration file, the A-REX should be restarted. If a cache is to be
removed and all data erased, it is recommended that the cache be put
in a \emph{draining} state until all currently running jobs possibly
accessing files in this cache have finished. In this state the cache
will not be used by any new jobs, but the hard links in the
\emph{joblinks} directory will be cleaned up as each job
finishes. Once this directory is empty it is safe to delete the entire
cache. See the \emph{cachedir} option in
Section~\ref{SubSection:ConfigFile} for how to set a cache to a
draining state.

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finishes (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}. The minumum value
for both parameters is 2 hours.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
-- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by using
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to
  the directory in which the SD is created. If \emph{path} is {*} the
  default sessiondir is used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} --
  specifies a directory to store cached data (see section
  \ref{sec:cache}). Multiple cache directories may be specified by
  specifying multiple \emph{cachedir} commands. Cached data will be
  distributed over multiple caches according to free space in
  each. Specifying no \emph{cachedir} command or commands with an
  empty path disables caching. The optional \textit{link\_path} specifies
  the path at which \emph{path} is accessible on computing nodes, if
  it is different from the path on the A-REX host. If
  \textit{link\_path} is set to '.'  files are not soft-linked, nor
  are per-job links created, but files are copied to the session
  directory. If a cache directory needs to be drained, then
  \emph{cachedir} should specify \emph{``drain''} as the
  \emph{link\_path}.
\item \textbf{\textit{remotecachedir}}\textit{=path {[}link\_path]} -
  specifies caches which are under the control of other A-REXs, but which
  this A-REX can have read-only access to (see
  Section~\ref{sec:remotecaches}).  Multiple remote cache directories may be
  specified by specifying multiple \emph{remotecachedir} commands. If
  a file is not available in paths specified by cachedir, the A-REX looks
  in remote caches. \emph{link\_path} has the same meaning as in
  \emph{cachedir}, but the special path ``replicate'' means files will
  be replicated from remote caches to local caches when they are requested.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} --
  specifies high and low watermarks for space used on the file system
  on which the cache directory is located, as a percentage of total
  file system capacity. When the max is exceeded, files will be
  deleted to bring the used space down to the min level. It is a good
  idea to have each cache on its own separate file system. To turn off
  this feature, \char`\"{}cachesize\char`\"{} without parameters can
  be specified. These cache settings apply to all caches specified by
  \emph{cachedir} commands.
\item \textbf{\textit{cacheloglevel}}\textit{=number} -- specified the
  level of logging by the \emph{cache-clean} tool, between 0 (FATAL)
  and 5 (DEBUG). Defaults to 3 (INFO).
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. The actual
number is provided in job description and defaults to 0.
\end{itemize}
